Windowed Developer Topic Analysis

### 2009-04-07 lda-paper.tex
some minor intro edits

Topic analysis of revisions in SCSs is important as often revisions
belonging to different topics are interleaved or even mixed inside of
commits.  Sometimes a single revision to a file contains multiple bug
fixes.  Using powerful topic analysis techniques like Latent Semantic
Indexing (LSI) or Latent Dirichlet Allocation (LDA) one can separate
these mixed comments into topics. These topics describe separate ideas
that are interleaved throughout the development. They indicate groups
of comments which are related to each other by their language, often
the content of the comments are related.  In this case a topic is a
set of tokens that are related to each other.

@@

One use of topic analysis is to help us partition a project's
time-line into periods of developer focus. By breaking apart an
iteration we may be able to recognize the underlying software
development process from these revision or at the very least what
maintenance was occurring in the repository at a particular time.

>>>>

Commits in SCSs are not necessarily consistent, they can have multiple
purposes, thus we hope that multipurposes manifest themselves as
topics interleaved within the commits.  Sometimes a single revision to
a file contains multiple bug fixes.  Others have demonstrated that by
using powerful topic analysis techniques like Latent Semantic Indexing
(LSI) or Latent Dirichlet Allocation (LDA) one can separate topics
from these mixed comments. These topics often describe separate ideas
that are interleaved throughout the development. A topic represents a
groups of commit comments which are related to each other by their
content.  In this case a topic is a set of tokens that are related to
each other.

@@

One use of topic analysis is to help us partition a project's
time-line into periods of developer focus. By breaking apart an
iteration into sets of topics and trends (topics which reoccur), we
may be able to recognize the underlying software development process
from these commits. Alternatively we can track down what maintenance was
occurring in the repository at a particular time.
